---
title: "Check experimental design"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

# Load the design and check level balance

The experimental design was created as part of the conjoint study in Qualtrics. Here we check to make sure that there is a balance across attribute levels (i.e., levels show up a roughly equal number of times for each attribute).

```{r load-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(here)

# Load design
design <- read_csv(here("data", "derived_data", "design.csv"))

# Check to make sure there is a balance across levels
as_tibble(design) %>%
  select(Organization:`Relationship with host government`) %>%
  gather(key = atts, value = lvls) %>%
  ggplot(aes(x = lvls)) +
  geom_bar() +
  facet_wrap(~ atts, scales = "free", nrow = 2)
```


# Dummy-code the design

Now we prepare the experimental design for use in estimating the model by dropping the first level of each attribute, which are all discrete, as the reference level.

```{r dummy-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
dummy_design <- as.data.frame(design)
for(i in 4:ncol(dummy_design)) {
  dummy_design[,i] <- as.factor(dummy_design[,i])
}

# Rename the variables.
colnames(dummy_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a dummy-coded version of all the attribute levels
dummy_design <- dummy_cols(
  dummy_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
)

# Rename the index variables
colnames(dummy_design)[4:15] <- c(
  str_c("org", 2:4), str_c("issue", 2:4), str_c("transp", 2),
  str_c("account", 2), str_c("fund", 2:3), str_c("gov_rel", 2:3)
)

# Save dummy-coded design output
write.csv(dummy_design, here("data", "derived_data", "dummy_design.csv"))
```


# Dummy-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.

```{r dummy-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# Rename the variables.
colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a dummy-coded version of all the attribute levels
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions
interactions <- interactions %>% 
  as_tibble() %>% 
  mutate(
    # Hypothesis 2b.
    amnesty_criticized = org1 * gov_rel2,
    greenpeace_criticized = org2 * gov_rel2,
    oxfam_criticized = org3 * gov_rel2,
    redcross_criticized = org4 * gov_rel2,
    amnesty_crackdown = org1 * gov_rel3,
    greenpeace_crackdown = org2 * gov_rel3,
    oxfam_crackdown = org3 * gov_rel3,
    redcross_crackdown = org4 * gov_rel3,
    # Hypothesis 3b.
    # emergency_criticized = issue1 * gov_rel2,
    environment_criticized = issue2 * gov_rel2,
    humanrights_criticized = issue3 * gov_rel2,
    refugees_criticized = issue4 * gov_rel2,
    # emergency_crackdown = issue1 * gov_rel3,
    environment_crackdown = issue2 * gov_rel3,
    humanrights_crackdown = issue3 * gov_rel3,
    refugees_crackdown = issue4 * gov_rel3,
    # Hypothesis 4b.
    # smalldonors_criticized = fund1 * gov_rel2,
    wealthydonors_criticized = fund2 * gov_rel2,
    govgrants_criticized = fund3 * gov_rel2,
    # smalldonors_crackdown = fund1 * gov_rel3,
    wealthydonors_crackdown = fund2 * gov_rel3,
    govgrants_crackdown = fund3 * gov_rel3,
    # Hypothesis 4c.
    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
    environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
    humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
    refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
    # Hypothesis 5b.
    # nottransp_criticized = transp1 * gov_rel2,
    transp_criticized = transp2 * gov_rel2,
    # nottransp_crackdown = transp1 * gov_rel3,
    transp_crackdown = transp2 * gov_rel3,
    # Hypothesis 5c.
    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
    # Hypothesis 5d.
    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    transp_environment_criticized = transp2 * issue2 * gov_rel2,
    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
    # Hypothesis 5e.
    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
  ) %>% 
  select(-contains("1"))

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "dummy_interactions.csv"))
```


# Index-code the design

Now we prepare the experimental design for use in estimating the model by keeping each level of each attribute, which are all discrete. An index-coded design has no reference levels.

```{r index-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
index_design <- as.data.frame(design)
for(i in 4:ncol(index_design)) {
  index_design[,i] <- as.factor(index_design[,i])
}

# Rename the variables.
colnames(index_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get an index-coded version of all the attribute levels
index_design <- dummy_cols(
  index_design,
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the index-coded variables
colnames(index_design)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Save index-coded design output
write.csv(index_design, here("data", "derived_data", "index_design.csv"))
```


# Index-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.

```{r index-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# Rename the variables
colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get an index-coded version of all the attribute levels
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the index-coded variables
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

# Build out all the necessary interactions
interactions <- interactions %>% 
  as_tibble() %>% 
  mutate(
    # # Hypothesis 2b.
    # amnesty_criticized = org1 * gov_rel2,
    # greenpeace_criticized = org2 * gov_rel2,
    # oxfam_criticized = org3 * gov_rel2,
    # redcross_criticized = org4 * gov_rel2,
    # amnesty_crackdown = org1 * gov_rel3,
    # greenpeace_crackdown = org2 * gov_rel3,
    # oxfam_crackdown = org3 * gov_rel3,
    # redcross_crackdown = org4 * gov_rel3,
    # Hypothesis 3b.
    emergency_criticized = issue1 * gov_rel2,
    environment_criticized = issue2 * gov_rel2,
    humanrights_criticized = issue3 * gov_rel2,
    refugees_criticized = issue4 * gov_rel2,
    emergency_crackdown = issue1 * gov_rel3,
    environment_crackdown = issue2 * gov_rel3,
    humanrights_crackdown = issue3 * gov_rel3,
    refugees_crackdown = issue4 * gov_rel3
    # # Hypothesis 4b.
    # smalldonors_criticized = fund1 * gov_rel2,
    # wealthydonors_criticized = fund2 * gov_rel2,
    # govgrants_criticized = fund3 * gov_rel2,
    # smalldonors_crackdown = fund1 * gov_rel3,
    # wealthydonors_crackdown = fund2 * gov_rel3,
    # govgrants_crackdown = fund3 * gov_rel3,
    # # Hypothesis 4c.
    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    # emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
    # emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    # environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
    # environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    # humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
    # humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    # refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
    # refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
    # # Hypothesis 5b.
    # nottransp_criticized = transp1 * gov_rel2,
    # transp_criticized = transp2 * gov_rel2,
    # nottransp_crackdown = transp1 * gov_rel3,
    # transp_crackdown = transp2 * gov_rel3,
    # # Hypothesis 5c.
    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    # transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    # transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    # transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    # transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    # transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    # transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
    # # Hypothesis 5d.
    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    # transp_emergency_criticized = transp2 * issue1 * gov_rel2,
    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    # transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    # transp_environment_criticized = transp2 * issue2 * gov_rel2,
    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    # transp_environment_crackdown = transp2 * issue2 * gov_rel3,
    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    # transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    # transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    # transp_refugees_criticized = transp2 * issue4 * gov_rel2,
    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    # transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
    # # Hypothesis 5e.
    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    # transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    # transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    # transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    # transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    # transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    # transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    # transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
    # transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
  )

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "index_interactions.csv"))
```


# Aggregate-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions. Here we do it by aggregating up the interaction terms.

```{r aggregate-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# # Rename the variables
# colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
# 
# # Use dummy_cols() to get an index-coded version of all the attribute levels
# interactions <- dummy_cols(
#   interactions, 
#   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
#   remove_first_dummy = FALSE,
#   remove_selected_columns = TRUE
# )
# 
# # Rename the index-coded variables
# colnames(interactions)[4:21] <- c(
#   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
#   str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
# )
#
# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown





# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
interactions <- interactions %>% 
  as_tibble() %>% 
  mutate(
    h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
    h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
    h2b_3 = h2b_1*h2b_2 # interaction term
    )




# Build out all the necessary interactions
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     # Hypothesis 2b.
#     amnesty_criticized = org1 * gov_rel2,
#     greenpeace_criticized = org2 * gov_rel2,
#     oxfam_criticized = org3 * gov_rel2,
#     redcross_criticized = org4 * gov_rel2,
#     amnesty_crackdown = org1 * gov_rel3,
#     greenpeace_crackdown = org2 * gov_rel3,
#     oxfam_crackdown = org3 * gov_rel3,
#     redcross_crackdown = org4 * gov_rel3,
#     # Hypothesis 3b.
#     emergency_criticized = issue1 * gov_rel2,
#     environment_criticized = issue2 * gov_rel2,
#     humanrights_criticized = issue3 * gov_rel2,
#     refugees_criticized = issue4 * gov_rel2,
#     emergency_crackdown = issue1 * gov_rel3,
#     environment_crackdown = issue2 * gov_rel3,
#     humanrights_crackdown = issue3 * gov_rel3,
#     refugees_crackdown = issue4 * gov_rel3,
#     # Hypothesis 4b.
#     smalldonors_criticized = fund1 * gov_rel2,
#     wealthydonors_criticized = fund2 * gov_rel2,
#     govgrants_criticized = fund3 * gov_rel2,
#     smalldonors_crackdown = fund1 * gov_rel3,
#     wealthydonors_crackdown = fund2 * gov_rel3,
#     govgrants_crackdown = fund3 * gov_rel3,
#     # Hypothesis 4c.
#     emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
#     emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
#     emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
#     environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
#     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
#     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
#     humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
#     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
#     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
#     refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
#     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
#     refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
#     # Hypothesis 5b.
#     nottransp_criticized = transp1 * gov_rel2,
#     transp_criticized = transp2 * gov_rel2,
#     nottransp_crackdown = transp1 * gov_rel3,
#     transp_crackdown = transp2 * gov_rel3,
#     # Hypothesis 5c.
#     nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
#     transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
#     nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
#     transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
#     nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
#     transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
#     nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
#     transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
#     nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
#     transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
#     nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
#     transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
#     # Hypothesis 5d.
#     nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
#     transp_emergency_criticized = transp2 * issue1 * gov_rel2,
#     nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
#     transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
#     nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
#     transp_environment_criticized = transp2 * issue2 * gov_rel2,
#     nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
#     transp_environment_crackdown = transp2 * issue2 * gov_rel3,
#     nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
#     transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
#     nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
#     transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
#     nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
#     transp_refugees_criticized = transp2 * issue4 * gov_rel2,
#     nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
#     transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
#     # Hypothesis 5e.
#     nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
#     transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
#     nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
#     transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
#     nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
#     transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
#     nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
#     transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
#     nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
#     transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
#     nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
#     transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
#     nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
#     transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
#     nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
#     transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
#   )

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
```


# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=90}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>  
