---
title: "Analysis and results"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

# Load packages

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)

# Set Stan options
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```


# Model calibration

After selecting the model we'd like to run, model calibration proceeds as follows. Note that model calibration is run in a separate R script given how long it takes to run each model. Model output can be loaded for analysis in the next section.

```{r model-calibration, eval=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load data and design
final_data <- read_rds(here::here("data", "derived_data", "final_data.rds"))
X <- read_rds(here::here("data", "derived_data", "final_design.rds"))

# Restructure choice data Y
Y <- final_data %>%
  select(contains("Q4")) %>%
  as.matrix()

# Restructure covariate matrix Z
if (intercept == 1) {
  Z <- matrix(data = 1, nrow = dim(X)[1], ncol = 1)
}
if (public_affairs == 1) {
  Z <- final_data %>%
    select(
      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7 # Public affairs
    )
}
if (political_ideology == 1) {
  Z <- final_data %>%
    select(
      Q5.2 # Political ideology
    )
}
if (social_views == 1) {
  Z <- final_data %>%
    select(
      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10 # Social views
    )
}
if (charity_voluntarism == 1) {
  Z <- final_data %>%
    select(
      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10 # Charity and voluntarism
    )
}
if (demographics == 1) {
  Z <- final_data %>%
    select(
      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17 # Demographics
    )
}
if (public_political == 1) {
  Z <- final_data %>%
    select(
      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
      Q5.2                                   # Political ideology
    )
}
if (public_political_social == 1) {
  Z <- final_data %>%
    select(
      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7, # Public affairs
      Q5.2,                                  # Political ideology
      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10         # Social views
    )
}
if (public_political_social_charity == 1) {
  Z <- final_data %>%
    select(
      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
      Q5.2,                                                            # Political ideology
      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10  # Charity and voluntarism
    )
}
if (public_political_social_charity_demo == 1) {
  Z <- final_data %>%
    select(
      Q2.1, Q2.2, Q2.3_1:Q2.3_7, Q2.4, Q5.7,                           # Public affairs
      Q5.2,                                                            # Political ideology
      Q5.6, Q5.11, Q5.8, Q5.9, Q5.10,                                  # Social views
      Q2.7, Q2.8, Q2.5, Q2.6, Q2.9, Q2.10, Q5.4, Q5.5, Q5.3_1:Q5.3_10, # Charity and voluntarism
      Q5.12, Q5.13, Q5.14, Q5.15, Q5.16_1:Q5.16_6, Q5.17               # Demographics
    )
}

# Replace factor labels with levels
Z <- Z %>%
  mutate_if(is.factor, as.integer) %>%
  mutate_if(is.integer, as.factor)

# Pad the variables names with _
colnames(Z) <- str_c(colnames(Z), "_")

# Use the output of lm to get a dummy-coded version of the covariate matrix Z
Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
out <- lm(y ~ ., Z, x = TRUE)

# Save out Z as a matrix, including an intercept
Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
  bind_cols(as_tibble(out$x[,-1])) %>%
  as.matrix()

# Specify the data for calibration in a list
data <- list(
  R = dim(X)[1],      # Number of respondents
  S = dim(X)[2],      # Number of choice tasks
  A = dim(X)[3],      # Number of choice alternatives
  I = dim(X)[4],      # Number of (estimable) attribute levels
  J = ncol(Z),        # Number of respondent-level covariates

  Gamma_mean = 0,      # Mean of population-level means
  Gamma_scale = 1,     # Scale of population-level means
  Omega_shape = 5,     # Shape of population-level scale
  tau_mean = 0,        # Mean of population-level scale
  tau_scale = 10,      # Scale of population-level scale

  Y = Y,               # Matrix of observed choices
  X = X,               # Array of experimental designs per choice task
  Z = Z                # Matrix of respondent-level covariates
)

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 42
)
run <- list(data = data, fit = fit)
if (intercept == 1) write_rds(run, here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

The model is calibrated using a non-centered parameterization of a hierarchical multinomial logit model.

```{stan hmnl-noncentered, output.var="hmnl_noncentered", eval=FALSE}
// Index values, hyperprior values, observations, and covariates.
data {
  int<lower = 1> R;                  // Number of respondents.
  int<lower = 1> S;                  // Number of choice tasks.
  int<lower = 2> A;                  // Number of choice alternatives.
  int<lower = 1> I;                  // Number of observation-level covariates.
  int<lower = 1> J;                  // Number of population-level covariates.

  real Gamma_mean;                   // Mean of population-level means.
  real<lower=0> Gamma_scale;         // Scale of population-level means.
  real<lower=0> Omega_shape;         // Shape of population-level scale.
  real tau_mean;                     // Mean of population-level scale.
  real<lower=0> tau_scale;           // Scale of population-level scale.

  int<lower = 1, upper = A> Y[R, S]; // Matrix of observations.
  matrix[A, I] X[R, S];              // Array of observation-level covariates.
  matrix[R, J] Z;                    // Matrix of population-level covariates.
}

// Parameters and hyperparameters.
parameters {
  matrix[J, I] Gamma;                // Matrix of population-level hyperparameters.
  corr_matrix[I] Omega;              // Population model correlation matrix hyperparameters.
  vector<lower = 0>[I] tau;          // Population model vector of scale hyperparameters.
  matrix[R, I] Delta;                // Matrix of non-centered observation-level parameters.
}

// Deterministic transformation.
transformed parameters {
  // Matrix of centered observation-level parameters.
  matrix[R, I] Beta;

  // Non-centered parameterization.
  for (r in 1:R) {
    Beta[r,] = Z[r,] * Gamma + Delta[r,] * quad_form_diag(Omega, tau);
  }
}

// Hierarchical multinomial logit model.
model {
  // Hyperpriors.
  to_vector(Gamma) ~ normal(Gamma_mean, Gamma_scale);
  Omega ~ lkj_corr(Omega_shape);
  tau ~ normal(tau_mean, tau_scale);

  // Non-centered population model and likelihood.
  for (r in 1:R) {
    Delta[r,] ~ normal(0, 1);
    for (s in 1:S) {
      Y[r, s] ~ categorical_logit(X[r, s] * Beta[r,]');
    }
  }
}

// Generated quantities conditioned on parameter draws.
generated quantities {
  // Compute log likelihood for model fit.
  matrix[R, S] log_lik;
  for (r in 1:R) {
    for (s in 1:S) {
      log_lik[r, s] = categorical_logit_lpmf(Y[r, s] | X[r, s] * Beta[r,]');
    }
  }
}
```


# Load data and model output

Once we specify the model we'd like to evaluate, the following analysis follows.

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit
```


# Model checking

```{r model-checking}
source(here::here("R", "stan_utility.R"))

# Gamma
draws_gamma <- fit %>% 
  extract(
    pars = str_c("Gamma[", 1:13, ",1]"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_gamma %>% 
  mcmc_hist_by_chain()

draws_gamma %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# Extract the Omega parameters only and look at trace plots, etc.

# Omega
draws_Omega <- fit %>% 
  extract(
    regex_pars = c("Omega"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_gamma %>% 
  mcmc_hist_by_chain()

draws_gamma %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# # Check diagnostics
# check_all_diagnostics(fit)

# Check for divergences
check_div(fit)

# # Check the effective sample size (NOT WORKING?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (NOT WORKING?)
# check_rhat(fit)

# Check trace plots (SUBSET?)
color_scheme_set("mix-blue-red")
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    pars = str_c("Gamma[", 1:13, ",1]"),
    n_warmup = 2000,
    facet_args = list(
      nrow = 2, 
      labeller = label_parsed
    )
  )

# ggsave(
#   "intercept_trace_noncentered.png",
#   path = here::here("analysis", "output", "figures"),
#   width = 12, height = 6, units = "in"
# )
```


# Extract draws

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Gamma[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```


# Plot marginals and contrasts

```{r plot-marginals}
#########

# Update covariate labels
# Add contrasts where appropriate (see hypotheses Rmd documents)

#########

intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 1                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load draws
if (intercept == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) draws <- read_rds(here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))

# Name labels
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
)

# Name covariates
if (public_affairs == 1) {
  covariate_labels <- c(
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No"
  )
}
if (political_ideology == 1) {
  covariate_labels <- c(
    "Liberal to Conservative"
  )
}
if (social_views == 1) {
  covariate_labels <- c(
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
    str_c(
      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    )
  )
}
if (charity_voluntarism == 1) {
  covariate_labels <- c(
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
    str_c(
      c(
        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      ), 
      "Member to Not"
    )
  )
}
if (demographics == 1) {
  covariate_labels <- c(
    str_c(
      "Gender: ", 
      c("Female", "Transgender", "Prefer not to say", "Other")
    ), 
    str_c(
      "Marital status: ", 
      c("Widowed", "Divorced", "Separated", "Never married")
    ), 
    "Education: Less than high school to Doctorate",
    "Income: Less than $10,000 to $300,000 or more",
    str_c(
      "Race/ethnicity: ", 
      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
    ),
    "Age: Under 18 to 85 or older"
  )
}
if (public_political == 1) {
  covariate_labels <- c(
    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative"
  )
}
if (public_political_social == 1) {
  covariate_labels <- c(
    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
    str_c(
      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    )
  )
}
if (public_political_social_charity == 1) {
  covariate_labels <- c(
    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
    str_c(
      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    ),
    # Charity and voluntarism
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
    str_c(
      c(
        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      ), 
      "Member to Not"
    )
  )
}
if (public_political_social_charity_demo == 1) {
  covariate_labels <- c(
    # Public affairs
    "Follow national news: Multiple times a day to Never", "Follow international news: Always to Never", 
    str_c(
      "Medium to follow news: ", 
      c("TV", "Print", "Online (excluding social media)", "Social media", "Radio", "Email newsletters", "News app")
    ),
    "Follow government and public affairs: Most of the time to Hardly at all", "Traveled to a developing country: No",
    # Political ideology
    "Liberal to Conservative",
    # Social views
    "Trust in political institutions: None to Complete", "People should be more charitable: Agree to Disagree",
    "Religious and worship service attendance: Multiple times a week to Never", "Importance of religion: Extremely to Not at all",
    str_c(
      "Religion: ", 
      c("Protestant", "Christian Orthodox", "Jewish", "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")
    ),
    # Charity and voluntarism
    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",
    "Donated last year: $1-$49 to $10,000 or more", "Volunteered in past 12 months: No", "Volunteer frequency: Weekly to Every few years",
    "History of activism: Extreme to Never", "History of family activism: Extreme to Never", 
    str_c(
      c(
        "Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      ), 
      "Member to Not"
    ),
    # Demographics
    str_c(
      "Gender: ", 
      c("Female", "Transgender", "Prefer not to say", "Other")
    ), 
    str_c(
      "Marital status: ", 
      c("Widowed", "Divorced", "Separated", "Never married")
    ), 
    "Education: Less than high school to Doctorate",
    "Income: Less than $10,000 to $300,000 or more",
    str_c(
      "Race/ethnicity: ", 
      c("White", "Black or African American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Pacific Islander", "Other")
    ),
    "Age: Under 18 to 85 or older"
  )
}

# Plot marginals
# if (intercept == 1) {
#   draws %>% 
#     mutate(
#       levels = factor(i, labels = level_labels)
#     ) %>%
#     ggplot(aes(x = Gamma, y = levels)) + 
#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#     # geom_halfeyeh(.width = .95) +
#     geom_vline(xintercept = 0, color = "grey") +
#     labs(y = "Attribute Levels")
# }

# if (intercept != 1) {
#   draws %>% 
#     filter(j != 1) %>% 
#     mutate(
#       levels = factor(i, labels = level_labels), 
#       covariates = factor(j, labels = covariate_labels)  
#     ) %>%
#     ggplot(aes(x = Gamma, y = covariates)) +
#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#        # geom_halfeyeh(.width = .95) +
#        geom_vline(xintercept = 0, color = "white") +
#        labs(y = "Covariates") +
#        facet_wrap(~ levels, ncol = 5)
# }

# # Save plot
# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
# ggsave(
#   file_name,
#   path = here::here("analysis", "output", "figures"),
#   width = ifelse(intercept == 1, 12, 20), 
#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
#   units = "in"
# )
```

As an experiment, it might be helpful to use a heatmap to identify where there are significant differences in the non-intercept models, which can then be narrowed down using the marginal plots.

```{r heatmaps}
if (public_affairs == 1) plot_title <- paste("Public Affairs")
if (political_ideology == 1) plot_title <- paste("Political Ideology")
if (social_views == 1) plot_title <- paste("Social Views")
if (charity_voluntarism == 1) plot_title <- paste("Covariates related to charity and voluntarism")
if (demographics == 1) plot_title <- paste("Demographics")
if (public_political == 1) plot_title <- paste("Public Affairs and Political Ideology")
if (public_political_social == 1) plot_title <- paste("Public Affairs, Political Ideology, and Social Views")
if (public_political_social_charity == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, and Charity and Voluntarism")
if (public_political_social_charity_demo == 1) plot_title <- paste("Public Affairs, Political Ideology, Social Views, Charity and Voluntarism, and Demographics")

if (charity_voluntarism == 1) {
  j_labels <- tribble(
    ~j, ~j_label,
    2, "Importance of trusting charities", 
    3, "Trust charities", 
    4, "Frequency of donation", 
    5, "Amount of donation", 
    6, "Volunteered", 
    7, "Volunteer frequency", 
    8, "Personal involvement in activism", 
    9, "Family involvement in activism", 
    10, "Membership in church", 
    11, "Membership in sports", 
    12, "Membership in art, music, or educational organization", 
    13, "Membership in labor union", 
    14, "Membership in political party", 
    15, "Membership in envrionmental organization", 
    16, "Membership in professional association", 
    17, "Membership in humanitarian organization", 
    18, "Membership in consumer organization", 
    19, "Membership in other organization"
  ) %>% 
    mutate(j_label = fct_inorder(j_label))
}

if (intercept != 1) {
  # Posterior means.
  posterior_means <- draws %>% 
    filter(j != 1) %>% 
    left_join(j_labels, by = "j") %>% 
    left_join(level_lookup, by = "i") %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      # covariates = factor(j, labels = covariate_labels)
      covariates = factor(j, labels = 1:length(covariate_labels))
    ) %>% 
    group_by(category, attribute, j_label) %>% 
    summarize(
      mean = mean(Gamma),
      ci_lower = quantile(Gamma, .025),
      ci_upper = quantile(Gamma, .975),
      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
    )
  
  # Heatmap of Gamma matrix.
  plot_heatmap <- posterior_means %>% 
    mutate(
      gt_lt_zero = gt_zero + lt_zero,
      Coefficients = factor(
        gt_lt_zero, 
        levels = -1:1,
        labels = c("Negative", "Not Significant", "Positive"))
    ) %>% 
    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
    geom_tile(color = "white", size = 0.25) +
    # scale_fill_brewer(palette = "Blues") +
    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
    scale_x_discrete(expand = c(0.001, 0.001)) +
    scale_y_discrete(expand = c(0.001, 0.001)) +
    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
    theme_ngo(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom",
          strip.placement = "outside") +
    labs(
      title = plot_title,
      x = "Covariates",
      y = "Attribute Levels"
    ) + 
    # facet_wrap(~ category, ncol = 1, scales = "free_y")
    facet_grid(vars(category), scales = "free_y", space = "free_y")
}

plot_heatmap
ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.pdf"),
       width = 26/3, height = 6.5, units = "in", device = cairo_pdf)
ggsave(plot_heatmap, filename = here("analysis", "output", "figures", "q2-heatmap.png"),
       width = 26/3, height = 6.5, units = "in", type = "cairo", dpi = 300)

# Save plot
if (public_affairs == 1) file_name <- paste("public-affairs_coefficient-matrix.png")
if (political_ideology == 1) file_name <- paste("political-ideology_coefficient-matrix.png")
if (social_views == 1) file_name <- paste("social-views_coefficient-matrix.png")
if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_coefficient-matrix.png")
if (demographics == 1) file_name <- paste("demographics_coefficient-matrix.png")
if (public_political == 1) file_name <- paste("public-political_coefficient-matrix.png")
if (public_political_social == 1) file_name <- paste("public-political-social_coefficient-matrix.png")
if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_coefficient-matrix.png")
if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_coefficient-matrix.png")
ggsave(
  file_name,
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div> 
